---
title: "Assignment 3"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```

The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.

```{r}

#setwd("C:\Program Files\R\R-3.6.2")

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("caret")

```
# Question 1

```{r}

dfc <- read_csv("assignment3Carvana.csv")
skim(dfc)

```
```{r}

set.seed(52156)

dfcTrain <- dfc %>% sample_frac(0.65)
dfcTest <- dplyr::setdiff(dfc, dfcTrain)

```
# Question 2

```{r}

# 2.a

boxPlotsForAuction <- dfc %>%
  ggplot(aes(x = BadBuy, y = MMRAauction, group = BadBuy)) +
  geom_boxplot()

boxPlotsForAuction

```
```{r}

boxPlotsForAge <- dfc %>%
  ggplot(aes(x = BadBuy, y = Age, group = BadBuy)) +
  geom_boxplot()

boxPlotsForAge

```
```{r}

boxPlotsForOdometer <- dfc %>%
  ggplot(aes(x = BadBuy, y = Odo, group = BadBuy)) +
  geom_boxplot()

boxPlotsForOdometer

```
```{r}

# 2.b

a <- table(dfc$Size, dfc$BadBuy)
report <- as.data.frame(a)
report <- spread(report, key = Var2, value = Freq)
report$Total = report$`0` + report$`1`
report <- setNames(report, c("Size", "Good_investment", "Lemons", "Total_cars"))
arrange(report, desc(report$Total_cars))

```
```{r}

dfc %>% 
  group_by(BadBuy) %>% 
  tally()

```
```{r}

report$Perc_of_lemons = report$Lemons/5003 * 100
arrange(report, desc(report$Perc_of_lemons))

```
# Question 3

```{r}

fitLPM  <- lm(BadBuy ~ ., data = dfcTrain)

summary(fitLPM)

```
```{r}

# 3.a

resultsTrain <- dfcTrain %>%
  			mutate(predictedBadBuy = predict(fitLPM, dfcTrain))

resultsTrain

```
```{r}

performanceTrain <- metric_set(rmse, mae)
performanceTrain(resultsTrain, truth = BadBuy, estimate = predictedBadBuy)

```
```{r}

resultsTest <- dfcTest %>%
  			mutate(predictedBadBuy = predict(fitLPM, dfcTest))

resultsTest

```
```{r}

performanceTest <- metric_set(rmse, mae)
performanceTest(resultsTest, truth = BadBuy, estimate = predictedBadBuy)

```
```{r}

# 3.c

colsToFactor <- c("BadBuy")
dfc <- dfc %>%
  mutate_at(colsToFactor, ~factor(.))

colsToFactor1 <- c("BadBuy")
dfcTrain <- dfcTrain %>%
  mutate_at(colsToFactor1, ~factor(.))

colsToFactor2 <- c("BadBuy")
dfcTest <- dfcTest %>%
  mutate_at(colsToFactor2, ~factor(.))

resultsTest1 <-
	fitLPM %>%
	predict(dfcTest, type = "response") %>%
	bind_cols(dfcTest, predictedProb = .) %>%
	mutate(predictedClass = as.factor(ifelse(predictedProb > 0.5, 1, 0)))

resultsTest1

```
```{r}

resultsTest1 %>%
  conf_mat(truth = BadBuy, estimate = predictedClass) %>% 
  autoplot(type = "heatmap")

```
```{r}

# 3.d

resultsTest1 %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
# Question 4

```{r}

colsToFactor <- c("Auction", "Make", "Color", "WheelType", "Size")
dfc <- dfc %>%
  mutate_at(colsToFactor, ~factor(.))

colsToFactor1 <- c("Auction", "Make", "Color", "WheelType", "Size")
dfcTrain <- dfcTrain %>%
  mutate_at(colsToFactor1, ~factor(.))

colsToFactor2 <- c("Auction", "Make", "Color", "WheelType", "Size")
dfcTest <- dfcTest %>%
  mutate_at(colsToFactor2, ~factor(.))

fitLGM1 <- train(BadBuy ~ ., family = "binomial", data = dfcTrain, method = "glm")

resultsCaret1 <-	fitLGM1 %>%
	predict(dfcTest, type = "raw") %>%
	bind_cols(dfcTest, predictedClass = .)

resultsCaret1

```
```{r}

resultsCaret1 %>%
  conf_mat(truth = BadBuy, estimate = predictedClass) %>% 
  autoplot(type = "heatmap")

```
```{r}

resultsCaret1 %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
```{r}

# install.packages("rockchalk")
library(rockchalk)

```

```{r}

# 4.a

dfc$Color <- combineLevels(dfc$Color, levs = c("NULL", "NOTAVAIL"), newLabel = "NULL")
dfc$Make <- combineLevels(dfc$Make, levs = c("ACURA", "CADILLAC", "LEXUS", "MINI", "SUBARU", "VOLVO"), newLabel = "OTHER")

set.seed(52156)

dfcTrain1 <- dfc %>% sample_frac(0.65)
dfcTest1 <- dplyr::setdiff(dfc, dfcTrain1)

```
```{r}

fitLGM2 <- train(BadBuy ~ ., family = "binomial", data = dfcTrain1, method = "glm")

resultsCaret2 <-	fitLGM2 %>%
	predict(dfcTest1, type = "raw") %>%
	bind_cols(dfcTest1, predictedClass = .)

resultsCaret2

```
```{r}

# 4.b & 4.c

summary(fitLGM2)

```
```{r}

# 4.d

fitLGMresults2 <-
	fitLGM2 %>%
	predict(dfcTest1, type = "raw") %>%
	bind_cols(dfcTest1, predictedProb = .) %>%
	mutate(predictedClass = as.factor(ifelse(predictedProb > 0.5, 1, 0)))

fitLGMresults2

```
```{r}

resultsCaret2 %>%
  conf_mat(truth = BadBuy, estimate = predictedClass) %>% 
  autoplot(type = "heatmap")

```

```{r}

resultsCaret2 %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
```{r}

# 4.e

resultsCaret2 %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1") %>% 
  tidy()

```
# Question 5

```{r}

# 5.a

set.seed(123)

fitLDA <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method = 'lda', trControl = trainControl(method = 'cv', number = 10))

resultsLDA <-	fitLDA %>%
	predict(dfcTest1, type = "raw") %>%
	bind_cols(dfcTest1, predictedClass = .)

resultsLDA

```
```{r}

resultsLDA %>%
  conf_mat(truth = BadBuy, estimate = predictedClass) %>% 
  autoplot(type = "heatmap")

```
```{r}

resultsLDA %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
```{r}

# 5.b.i

library(class)

set.seed(123)

fitKNN <- train(BadBuy ~ ., data=dfcTrain1, method = 'knn', preProcess = c("center","scale"), trControl = trainControl(method = 'cv', number = 10), tuneLength = 10)

plot(fitKNN)

```
```{r}

#5.b.iii

resultsKNN <-	fitKNN %>%
	predict(dfcTest1, type = "raw") %>%
	bind_cols(dfcTest1, predictedClass = .)

resultsKNN

```
```{r}

resultsKNN %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
```{r}

# 5.c.i

lambdaValues <- 10^seq(-5, 2, length = 100)

set.seed(123)

fitLasso <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method = 'glmnet', trControl = trainControl(method = 'cv', number = 10), tuneGrid = expand.grid(alpha = 1, lambda = lambdaValues))

varImp(fitLasso)$importance %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Importance = scales::percent(Overall/100)) %>% 
  arrange(desc(Overall)) %>% 
  as_tibble()

```
```{r}

# 5.c.ii

plot(varImp(fitLasso), top = 25)

```
```{r}

# 5.c.iii

fitLasso$bestTune$lambda

```
```{r}

# 5.c.iv

resultsLasso <- 
  fitLasso %>%
  predict(dfcTest1, type = 'raw') %>%
  bind_cols(dfcTest1, predictedClass = .)

resultsLasso %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = '1')

```
```{r}

# 5.d

lambdaValues <- 10^seq(-5, 2, length = 100)

set.seed(123)

fitRidge <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method = 'glmnet', trControl = trainControl(method = 'cv', number = 10), tuneGrid = expand.grid(alpha = 0, lambda = lambdaValues))

varImp(fitRidge)$importance %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Importance = scales::percent(Overall/100)) %>% 
  arrange(desc(Overall)) %>% 
  as_tibble()

```
```{r}

plot(varImp(fitRidge), top = 25)

```
```{r}

fitRidge$bestTune$lambda

```
```{r}

resultsRidge <- 
  fitRidge %>%
  predict(dfcTest1, type = 'raw') %>%
  bind_cols(dfcTest1, predictedClass = .)

resultsRidge %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = '1')

```
```{r}

lambdaValues <- 10^seq(-5, 2, length = 100)

set.seed(123)

fitElastic <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method='glmnet', trControl = trainControl(method = 'cv', number = 10), tuneGrid = expand.grid(alpha = 0.5, lambda=lambdaValues))

varImp(fitElastic)$importance %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Importance = scales::percent(Overall/100)) %>% 
  arrange(desc(Overall)) %>% 
  as_tibble()

```
```{r}

plot(varImp(fitElastic), top = 25)

```
```{r}

fitElastic$bestTune$lambda

```
```{r}

resultsElastic <- 
  fitElastic %>%
  predict(dfcTest1, type='raw') %>%
  bind_cols(dfcTest1, predictedClass=.)

resultsElastic %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = '1')

```
```{r}

# 5.e.i

set.seed(123)

fitQDA <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method = 'qda', trControl = trainControl(method = 'cv', number = 10))

resultsQDA <-	fitQDA %>%
	predict(dfcTest1, type = "raw") %>%
	bind_cols(dfcTest1, predictedClass = .)

resultsQDA

```
```{r}

resultsQDA %>%
  conf_mat(truth = BadBuy, estimate = predictedClass) %>% 
  autoplot(type = "heatmap")

```
```{r}

resultsQDA %>% 
  xtabs(~predictedClass + BadBuy, .) %>% 
  confusionMatrix(positive = "1")

```
```{r}

# 5.f

options(yardstick.event_first = FALSE)

# install.packages("cowplot")
library(cowplot)

fitLPMCopy <- resultsTest1 %>%
  mutate(model = "m1")

fitLGM1Copy <- resultsCaret1 %>%
  mutate(model = "m2")

fitLGM2Copy <- resultsCaret2 %>% 
  mutate(model = "m3")

fitLDACopy <- resultsLDA %>% 
  mutate(model = "m4")

fitLassoCopy <- resultsLasso %>% 
  mutate(model = "m5")

fitRidgeCopy <- resultsRidge %>% 
 mutate(model = "m6")

fitElasticCopy <- resultsElastic %>% 
  mutate(model = "m7")

fitQDACopy <- resultsQDA %>%
  mutate(model = "m8")

fitKNNCopy <- resultsKNN %>%
  mutate(model = "m9")

glmOutAll <- bind_rows(fitLPMCopy, fitLGM1Copy,fitLGM2Copy, fitLDACopy, fitLassoCopy, fitRidgeCopy, fitElasticCopy, fitQDACopy, fitKNNCopy)
glmOutAll$predictedClass <- as.numeric(glmOutAll$predictedClass)

glmOutAll %>%
  group_by(model) %>%
  roc_curve(truth = BadBuy, predictedClass) %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = model)) + 
  geom_line(size = 1.1) +
  geom_abline(slope = 1, intercept = 0, size = 0.4) +
  scale_color_manual(values = c("#CC0000", "#006600", "#669999", "#00CCCC", 
                             "#660099", "#CC0066", "#FF9999", "#FF9900", 
                             "black", "black", "black", "black", "black")) +
  coord_fixed() +
  theme_cowplot()

```
```{r}

glmOutAll %>%
  group_by(model) %>%
  roc_auc(truth = BadBuy, predictedClass)

```
```{r}

# Bonus question

# install.packages("grplasso")
library(grplasso)

```
```{r}

set.seed(123)

dfTrainGroup <-
  dfcTrain1 %>%
  mutate(BadBuy = as.numeric(BadBuy)) %>% 
  mutate(BadBuy = ifelse(BadBuy == 2, 1, 0))

fitGroupedLasso1 <- grplasso(BadBuy ~ ., data = dfTrainGroup, model = LogReg(), lambda = 50)

fitGroupedLasso1$coefficients

```
```{r}

fitGroupedLasso2 <- grplasso(BadBuy ~ ., data = dfTrainGroup, model = LogReg(), lambda = 100)

fitGroupedLasso2$coefficients

```
```{r}

fitLasso1 <- train(BadBuy ~ ., family = 'binomial', data = dfcTrain1, method = 'glmnet', trControl = trainControl(method = 'cv', number = 10), tuneGrid = expand.grid(alpha = 1, lambda = 0.01))

coefficients(fitLasso1)

```

